Covariance as constraint: Leveraging leaf economic relationships to constrain plant functional type trait estimates

### 2018-01-08 manuscript-md/02_methods.Rmd
Simplify mean and CI sentence in methods (Dietze)

To assess the impact of multivariate and hierarchical constraint on trait estimates,
we compared the mean and size of the 95% confidence intervals of mean estimates of each trait for each PFT from each model (Fig.\ \@ref(fig:meancompare)).
In addition, we report the mean and 95% confidence intervals of mean estimates for each trait and PFT from the hierarchical model in tabular form (Tab.\ 3 and 4).

>>>>

To assess the impact of multivariate and hierarchical constraint on trait estimates,
we compared the mean and 95% confidence intervals of trait estimates for each PFT from each model (Fig.\ \@ref(fig:meancompare)).
